---
title: "WUP_04"
author: "Kimberly Lemus Munoz"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSScsv <-read.csv("GSScsv.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(GSScsv,aes(x=DEGREE,WORDSUM))

basicCN + geom_boxplot()
```


The graph shows demonstrates a difference in wordsum test scores between grade levels.A visual that help see the different is,if we take the box of high school slide over the Junior college it goes underneath the junior college.In which makes it different between these two.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=GSScsv)
```


The mean of the graduate students is 2.25 above the mean of LT high school students.The Q1 graduate students is 10.Which is a larger than the Q3 of high school students which is 9.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSScsv)
summary.aov(model1)
```

The possibility of getting results that  have no difference between subgroups is 2.36 out of 10,000.This make us think  there is a different in the test scores between the subgroups.If we have the P-value we want to see what are different from one another.Next we will use the t test to see the different between them.


```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3,16.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

If any of the confidence interval that do not reach the 0 they are different.The comparison with the LT high school to the graduate is shown to be different because they don't reach 0.High school compared to graduate is different because it does not reach the 0 either.



```{r}
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
  
  
  The mean of LT high school studnets is compared to the men of graduate students is 2.25 lower.The first inferential test showed us that in that chances of getting these results if there was no difference is a 2.36 out of 10,000 chance: Finally, we compared the results of grade levels through a tukey test which showed there was a difference between High School and Graduate results and LT High School and Graduate results neither of the confidence intervals reached 0.
